Quantitative Evaluation of Touch-Screen Performance with Transition Matrix Measures

### 2015-08-26 flux-entropy-paper/flux-entropy-paper.tex
added a few refs

@@

>>>>

\begin{itemize}
\item Using Markov chains and transition matrices for usability
  modelling~\cite{Thimbleby:2001kq,Thimbleby:2004fj}
\item coding livecoding~\cite{Swift:2014tya}
\end{itemize}

@@

\section{A Corpus of Musical Touch-Screen Interactions}

In the following sections, we will use transition matrices, flux, and
entropy to analyse a corpus of data collected as part of our research
into collaborative interactions with musical touch-screen tablet
interfaces. In a period of more than two years (April 2013 - June 2015), we have
collected data from $139$ sessions where various participants used
musical touch-screen interfaces on Apple iPad devices. Each session
took place in a number of contexts including rehearsals, performances, lab study
sessions, classes, and casual demonstrations. Participants performed
free improvisations as well as written compositions and performed on
iPads alone or using setups of iPads and acoustic percussion
instruments. The median length of these sessions was 7m32s (minimum was
1m0s and maximum was 26m) and the
median number of participants was four (minimum 1, maximum 9).
